External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise n to be additive white Gaussian noise (AWGN). Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.). According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}. One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.

@@

In the last decade, there are many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem. These methods can be applied to real noisy image denoising directly. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising. ``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.

@@

\section{Conclusion and Future Work}

Image priors are important for solving image denoising problems. The external priors learned from external clean images are generally effective to most images, while the internal priors learned directly from the noisy image are adaptive to the given image but would be biased by the complex noise in real noisy images. In this paper, we demonstrates that, once unifying both the priors in external clean images and internal noisy images, we can achieve much better while still efficient performance on real image denoising problem. Specifically, the external patch group (PG) priors learned on natural clean images can be used to guide the subspace selection and orthogonal dictionary learning of internal noisy PGs from given noisy images. The experiments on real image denoising problem have demonstrated the powerful ability of the proposed method. In the future, we will speed up the proposed algorithm and evaluate the proposed method on other computer vision tasks such as image super-resolution.

>>>>

Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN). Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.). According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise. As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}. One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.

@@

Recently, several denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise in noisy images. These methods can be directly applied to denoise real noisy images. Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}. Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank MoG model. There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}. The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means. The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly. Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or mixture of Gaussians (MoG) to model the noise in real noisy images. However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.

@@

\section{Conclusion}

In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise. However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions. In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models. Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image. The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising. Experiments on two real noisy image datasets demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
